A Multi-Modal Model of Object Deformation under Robotic Pushing

### 2017-01-25 twostagedo-rev-final.tex
Constraints...

\subsubsection{Preservation of Area}
This constraint is applied per triangle in the mesh.  Since Teschner and Morris
found that the use of damping for the preservation of areas does not significantly improve the stability of the simulation, it is not included here either.  Therefore the force $\vec{F}^i_A$ is derived from the constraint and \eref{eq:EForce}: 
\begin{align}
 C &= \frac{\frac{1}{2}|(\vec{p}_j-\vec{p}_i)\times(\vec{p}_k-\vec{p}_i)|-A_0}{A_0}
\end{align}
where $A_0$ is the initial area of the triangle and $k_A$ the proportionality constant.

\subsubsection{Preservation of Angles}
The previous terms can not do anything to restore the mesh if triangles get flipped during deformation, which is not a valid state since the mesh models the surface of a 3D object.  For this reason we included a new term that enforces the preservation of the original angles of the triangles.  [\fref{fig:forces}(c)] gives an idea of how these forces look.  Here the energy depends on the difference between the current angle, between adjacent edges, and the angle between them at the equilibrium position. Energy is given by\footnote{It was also considered to multiply $E_\varphi$ by the lengths of the edges, but it hasn't improved the performance of the model.}:
\begin{align}
 E_\varphi(\varphi) & = \frac{1}{2}k_\varphi(\varphi - \varphi_0)^2 \\
 \varphi(p_i,p_j,p_k) & = \arccos \left( \dfrac{(p_j - p_i) \cdot (p_k - p_i)}{ \left\| p_j - p_i \right\| \left\|p_k - p_i \right\|} \right)^2 \nonumber
\end{align}

where $\varphi$ is the angle between adjacent edges, $E_\varphi$ is the energy associated with changes in the angle, $k_\varphi$ is the corresponding stiffness constant, and the $p_i$s are the Cartesian coordinates of the mass particles.

@@

The force is derived from:  %An additional line in the code also forces an inverted angle to recover its original orientation.
\begin{align}
 F_\varphi(p_i) & = k_\varphi(\varphi - \varphi_0)\dfrac{\partial \varphi}{\partial p_i} \\
 \dfrac{\partial \varphi}{\partial p_i} & = \dfrac{\partial}{\partial p_i} arccos \left(\frac{(\vec{p}_j-\vec{p}_i)\cdot(\vec{p}_k-\vec{p}_i)}{\left\|\vec{p}_j-\vec{p}_i\right\|\left\|\vec{p}_k-\vec{p}_i\right\|}\right) \displaybreak[0] \\
\end{align}

>>>>

\subsubsection{Preservation of Area}
The constraint for the potential energy is given by:
\begin{align}
 C &= \frac{\frac{1}{2}|(\vec{p}_j-\vec{p}_i)\times(\vec{p}_k-\vec{p}_i)|-A_0}{A_0}
\end{align}
where $A_0$ is the initial area of the triangle.  This constraint is applied per triangle in the mesh.  Since Teschner and Morris found that the use of damping for the preservation of areas does not significantly improve the stability of the simulation, it is not included here either.  Therefore the force $\vec{F}^i_A$ is derived from the constraint and \eref{eq:EForce} as shown in the appendix.

\subsubsection{Preservation of Angles}
The previous terms can not do anything to restore the mesh if triangles get flipped during deformation, which is not a valid state since the mesh models the surface of a 3D object.  For this reason we included a new term that enforces the preservation of the original angles of the triangles.  [\fref{fig:forces}(c)] gives an idea of how these forces look.  Here the energy depends on the difference between the current angle, between adjacent edges, and the angle between them at the equilibrium position. The constraint for this potential energy is given by\footnote{It was also considered to multiply $E_\varphi$ by the lengths of the edges, but it hasn't improved the performance of the model.}:
\begin{align}
 %E_\varphi(\varphi) & = \frac{1}{2}k_\varphi(\varphi - \varphi_0)^2 \\
 C &= \varphi - \varphi_0 \\
 \varphi(p_i,p_j,p_k) & = \arccos \left( \dfrac{(p_j - p_i) \cdot (p_k - p_i)}{ \left\| p_j - p_i \right\| \left\|p_k - p_i \right\|} \right)^2 \nonumber
\end{align}
where $\varphi$ is the angle between adjacent edges,% $E_\varphi$ is the energy associated with changes in the angle, $k_\varphi$ is the corresponding stiffness constant, 
and the $p_i$s are the Cartesian coordinates of the mass particles.

@@

The force is derived from:  %An additional line in the code also forces an inverted angle to recover its original orientation.
\begin{align}
 F_\varphi(p_i) & = k_\varphi(\varphi - \varphi_0)\dfrac{\partial \varphi}{\partial p_i} \\
 \dfrac{\partial \varphi}{\partial p_i} & = \dfrac{\partial}{\partial p_i} arccos \left(\frac{(\vec{p}_j-\vec{p}_i)\cdot(\vec{p}_k-\vec{p}_i)}{\left\|\vec{p}_j-\vec{p}_i\right\|\left\|\vec{p}_k-\vec{p}_i\right\|}\right) \displaybreak[0] \\
\end{align}
where $k_\varphi$ is the corresponding stiffness constant.
